# Introduction
This page is an output from the '[Productive R Workflow](https://www.productive-r-workflow.com/r/module2/format-text-with-markdown)' course, by Yann Holtz

# Data and Libraries


```{r}
#| label: libraries
library(tidyverse)
library(palmerpenguins)
```


```{r}
#| label: load-functions
source(file = "R/functions.r")
```

```{r}
#| label: load-data




# read clean data

df_clean_data <- readRDS(file = "input/df_clean_data.rds")

#Summary
summary(df_clean_data)

# Calculating mean bill length for different species and islands using dplyr
df_clean_data |>
  dplyr::filter(species == "Adelie") |>
  group_by(island) |>
  summarize(
    mean_bill_length = num(mean(bill_length_mm, na.rm = TRUE), digits = 2)
  )

# Use function in functions.r

create_scatterplot(df_clean_data, "Adelie", "Torgersen") 


```

## Data Source

```{r}
citation("palmerpenguins")
```

The `palmerpenguins` package was created and shared by Kristen Gorman, a researcher at the Palmer Station in Antarctica. It contains data about 344 penguins, including three species of penguins on three different islands. The package is licensed under a [CC-0](https://creativecommons.org/public-domain/cc0/) license.


# Descriptive Stats